---
title: 'ADDRESSING POSITIVITY VIOLATIONS WITH INCREMENTAL PROPENSITY SCORE INTERVENTIONS'
output: html_document
date: "`r format(Sys.Date(), '%B %d, %Y')`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(ggplot2)
library(ggrepel)
library(ggtext)
library(ggpubr)
library(showtext)
library(png)
library(grid)
library(gridExtra)
library(cowplot)

library(data.table)
library(glmnet)

library(knitr)
library(kableExtra)

library(tictoc)


library(rpart)
library(randomForest)
library(mgcv)
library(SuperLearner)
```



```{r}
source("thesis_functions.R")
# when updating and reloading the functions, the simulation- and estimator list also needs to be updated/ run again
```



# .

# SETUP

## DGPs

```{r}
# simulated data generating processes
sim_processes <- list(
  no = sim_no,
  prac = sim_prac,
  struc = sim_struc,
  struc_prac = sim_struc_prac
)

sim_titles <- c(
  no = "No Positivity Violations",
  prac = "Practical Positivity Violations",
  struc = "Structural Positivity Violations",
  struc_prac = "Combined Positivity Violations"
)
```


## PLOTTING TRUE PSs

```{r}
ps_colors_neon <- c(
  no          = "#00FFAA",  
  struc       = "#FF00EF",  
  prac        = "#FF2A00",  
  struc_prac  = "#00E5FF" 
)

ps_colors <- c(
  no          = "#596BE4FF",
  prac        = "#BF7CF6FF",
  struc       = "#9FD3CEFF",
  struc_prac  = "#BEC8ECFF"
)

ps_linetypes <- c(
  no = "solid",
  prac = "solid",
  struc = "dotdash",
  struc_prac = "twodash"
)

ps_labels <- c(
  no = "No",
  prac = "Practical",
  struc = "Structural",
  struc_prac = "Combined"
)
```


```{r}
# sampling nn covariates to plot the true PSs
nn <- 4e2
is_discrete <- FALSE

if (is_discrete) {
  W <- sample(0:4, size = nn, replace = TRUE)
  W_out <- (W == 3)
} else {
  W <- runif(nn, 0, 4)
  W_out <- (2 < W & W < 3)
}

# defining the true PSs
g1_no <- plogis(-2 + W)

g1_prac <- plogis(-4 + W)

g1_struc <- g1_no
g1_struc[W_out] <- 0

g1_struc_prac <- g1_prac
g1_struc_prac[W_out] <- 0


ps_plot <- data.table(
  W          = W,
  no         = g1_no,
  prac       = g1_prac,
  struc      = g1_struc,
  struc_prac = g1_struc_prac
)

ps_dt <- melt(ps_plot,
              id.vars = "W",
              variable.name = "method",
              value.name = "g")
```



```{r, fig.width=8, fig.height=5}
ps_dt[, g_plot := g]
ps_dt[method %in% c("struc", "struc_prac") & g == 0, g_plot := NA]
ps_dt[, method := factor(method, levels = c("no", "prac", "struc_prac", "struc"))]

flat_dt <- ps_dt[is.na(g_plot)]

# plotting the true PSs
ps_plot <- ggplot(
  ps_dt,
  aes(
    x = W,
    y = g_plot,
    color = method,
    linetype = method
    )
  ) +
  
  geom_hline(
    yintercept = seq(0, 1, by = 0.2),
    color = "grey91",
    linewidth = 0.4
  ) +
  
  geom_line(linewidth = 1.5) +
  
  geom_line(
    data = flat_dt,
    aes(y = 0),
    linewidth = 1.5
  ) +
  
  scale_color_manual(
    values = ps_colors,
    breaks = c("no", "prac", "struc", "struc_prac"),
    labels = ps_labels
  ) +
  
  scale_linetype_manual(
    values = ps_linetypes,
    breaks = c("no", "prac", "struc", "struc_prac"),
    labels = ps_labels
  ) +
  
  scale_x_continuous(
    breaks = seq(0, 4, 1),
    expand = expansion(mult = 0, add = 0.02)
  ) +
  
  scale_y_continuous(
    limits = c(0, 1),
    breaks = seq(0, 1, 0.2),
    expand = expansion(mult = 0, add = 0.02)
  ) +
  
  labs(
    title = "True Propensity Scores",
    x = "W",
    y = expression(P(A==1 ~ "|" ~ W)),
    color = NULL,
    linetype = NULL
  ) +
  
  theme_light(base_size = 16) +
  theme(
    # panel.grid = element_blank(),
    panel.border = element_blank(),
    plot.title = element_text(face = "bold", size = 18, hjust = 0),
    plot.title.position = "plot",
    
    axis.text = element_text(size = 16),
    axis.title = element_text(size = 16),
    legend.text = element_text(size = 16),
    legend.title = element_text(size = 16),
    
    legend.position = "bottom",
    legend.justification = 0
  ) +
  
  guides(
    color = guide_legend(
      title = "Violations:",
      nrow = 1
    ),
    linetype = guide_legend(
      title = "Violations:",
      nrow = 1,
      override.aes = list(
        linewidth = 2,
        linetype = "solid"
      )
    )
  )


ggsave(
  filename = "true_propensity_scores.png",
  plot = ps_plot,
  width = 8,
  height = 5,
  dpi = 300
)

ps_plot
```

```{r}
plogis(-2)
plogis(2)

plogis(-4)
plogis(0)
```



## TARGETS

```{r}
# https://r-graph-gallery.com/color-palette-finder
# Flourite
# colors <- c(
#   "#596BE4FF",
#   "#3FE6F8FF",
#   "#202841FF",
#   "#957BF9FF",
#   "#BF7CF6FF",
#   "#332A91FF",
#   "#1F76AFFF",
#   "#6FB7B2FF",
#   "#9FD3CEFF",
#   "#F2B97AFF",
#   "#E89A4FFF",
#   "#0B4F7AFF",
#   "#62A7BDFF"
# )


target_colors <- c(
  standard  = "#332A91FF",
  truncated = "#BF7CF6FF",
  trimmed   = "#1F76AFFF",
  rit       = "#596BE4FF",
  itt       = "#957BF9FF",
  ips       = "#6FB7B2FF"
)
```


## ESTIMATORS

```{r}
estimators <- list(
  iptw = list(
    name = "IPTW",
    targets = list(
      standard  = iptw_standard,
      truncated = iptw_trunc,
      trimmed   = iptw_trim,
      rit       = iptw_rit,
      itt       = iptw_itt,
      ips       = iptw_ips
    )
  ),
  
  iptw_hajek = list(
    name = "HAJEK",
    targets = list(
      standard  = iptw_hajek_standard,
      truncated = iptw_hajek_trunc,
      trimmed   = iptw_hajek_trim,
      rit       = iptw_hajek_rit,
      itt       = iptw_hajek_itt,
      ips       = iptw_hajek_ips
    )
  ),
  
  onestep = list(
    name = "OSE",
    targets = list(
      standard  = onestep_standard,
      truncated = onestep_trunc,
      trimmed   = onestep_trim,
      rit       = onestep_rit,
      itt       = onestep_itt,
      ips       = onestep_ips
    )
  ),
  
  tmle = list(
    name = "TMLE",
    targets = list(
      standard  = tmle_standard,
      truncated = tmle_trunc,
      trimmed   = tmle_trim,
      rit       = tmle_rit,
      itt       = tmle_itt,
      ips       = tmle_ips
    )
  )
  
)
```


## PARAMETERS

```{r}
alpha_vals <- c(1e-6, 0.01, 0.02, 0.03, 0.04, 0.05)
delta_vals <- c(1e-6, 1, 2, 3, 4, 10)
```



# .
# TARGET PARAMETERS


```{r}
target_parameter_mc_simulation <- function(is_discrete, sample_sizes, m) {
  # timing this function
  tic()
  
  # desired figure width and figure height so that the margin fits
  figw <- 8
  figh <- 5

  type_label <- if (is_discrete) "discrete" else "continuous"
  do_bars <- length(sample_sizes) > 1
  
  plots_by_n <- list()
  
  
  for (n in sample_sizes) {
    n_label <- paste0("n1e", log10(n))
    
    results <- list()
    plots <- list()
    
    
    for (name in names(sim_processes)) {
      # cat(sim_titles[name], "\n")
      
      m_results <- vector("list", m)
      
      for (i in 1:m) {
        sim <- sim_processes[[name]](n, is_discrete = is_discrete)
        # run monte carlo and add columns to store iteration number and data generating process
        res <- run_oracles(sim, alpha_vals, delta_vals)[, `:=`(positivity = name, sample_size = n, draw = i)]
        m_results[[i]] <- res
      }
      
      m_results <- rbindlist(m_results)
      aggr_m_results <- m_results[, .(
        psi = mean(psi),
        sd_psi = sd(psi),
        se_psi = sd(psi)/sqrt(m)
        ),
        by = .(positivity, sample_size, method, parameter, type)]
      
      results[[name]] <- aggr_m_results
      oracle_plot_data <- make_plot_data(aggr_m_results)
      
      # match method to color
      methods <- unique(oracle_plot_data$results_plot$method)
      targets <- get_target(methods)
      cols <- target_colors[targets]
      method_colors <- setNames(cols, methods)
      
      
      p <- plot_methods(
        oracle_plot_data,
        paste0(sim_titles[name], " (n = 1e", log10(n), ", m=", m, ")"),
        method_colors,
        y_label = "Target Value",
        bars = do_bars
      )
      
      plots[[name]] <- p
      
      # saving plot
      ggsave(
        filename = paste0("oracles_", n_label, "_", type_label, "_m", m, "_",  name, ".png"),
        plot = p,
        width = figw,
        height = figh,
        dpi = 300
      )
    }
  
  
    # saving results data
    results <- rbindlist(results, fill = TRUE)
    fwrite(results, paste0("oracles_", n_label, "_", type_label, "_m", m, "_results.csv"))
    
    # combining plots
    p_all <- plot_grid(
      plots$no,
      plots$prac,
      plots$struc,
      plots$struc_prac,
      nrow = 2
    )
    
    # saving combined plot
    ggsave(
      filename = paste0("oracles_", n_label, "_", type_label, "_m", m, "_all.png"),
      plot = p_all,
      width = 2 * figw,
      height = 2 * figh,
      dpi = 300
    )
    
    plots_by_n[[paste0("n_1e", log10(n))]] <- plots
    print(p_all)
  }
  
  elapsed <- toc(quiet = TRUE)
  cat(
    "sample_sizes =",
    paste(format(sample_sizes, scientific = TRUE), collapse = ", "),
    ", m =", m,
    "~",
    round(elapsed$toc - elapsed$tic, 2),
    "seconds\n"
  )
  # error bars are \pm sd_psi = sd(psi), that is standard deviation over monte carlo runs
}
```


## [1] SINGLE LARGE

```{r, fig.width=16, fig.height=10}
target_parameter_mc_simulation(
  is_discrete = FALSE,
  sample_sizes = c(1e8),
  m = 1
)
# sample_sizes = 1e+07 , m = 1 ~ 30.14 seconds
# sample_sizes = 1e+08 , m = 1 ~ 1168.96 seconds
```


## [2] MC AVERAGING


```{r, fig.width=16, fig.height=10}
target_parameter_mc_simulation(
  is_discrete = FALSE,
  sample_sizes = c(1e1, 1e2, 1e3, 1e4),
  m = 500
)
# sample_sizes = 1e+01, 1e+02, 1e+03, 1e+04 , m = 200 ~ 21.62 seconds
# sample_sizes = 1e+01, 1e+02, 1e+03, 1e+04 , m = 500 ~ 35.57 seconds
```


## 2x2 GRID PLOT

```{r}
make_2x2_grid_plot <- function(is_discrete, sample_sizes, m) {
  tic()

  type_label <- if (is_discrete) "discrete" else "continuous"
  n_labels <- paste0("n1e", log10(sample_sizes))
    
  # selecting plots to combine
  files <- paste0(
    "oracles_", n_labels, "_", type_label, "_m", m, "_all.png"
  )
  
  # desired figure width and figure height so that the margin fits
  figw <- 8
  figh <- 5
  
  # grab plots
  plots <- lapply(files, function(file) {
    plot <- rasterGrob(readPNG(file), interpolate = TRUE)
    ggdraw() +
      draw_grob(plot, x = 0, y = 0, width = 1, height = 1)
  })
  
  # combine plots to summary plot
  p_summary <- plot_grid(
    plotlist = plots,
    nrow = 2
  )
  
  
  ggsave(
    filename = paste0("oracles_", type_label, "_m", m, "_2x2_grid.png"),
    plot = p_summary,
    width = 4 * figw,
    height = 4 * figh,
    dpi = 300
  )
  
  elapsed <- toc(quiet = TRUE)
  cat(
    "sample_sizes =",
    paste(format(sample_sizes, scientific = TRUE), collapse = ", "),
    ", m =", m,
    "~",
    round(elapsed$toc - elapsed$tic, 2),
    "seconds\n"
  )

}
```


```{r, fig.width=32, fig.height=20}
make_2x2_grid_plot(
  is_discrete = FALSE,
  sample_sizes = c(1e1, 1e2, 1e3, 1e4),
  m <- 500
)
# sample_sizes = 1e+01, 1e+02, 1e+03, 1e+04 , m = 200 ~ 8.83 seconds
```



# .
# ESTIMATORS

```{r}
# CHECKING IF ORACLE SELECTION IS CORRECT

# loading precomputed oracles
  res_oracles_test <- fread("oracles_n1e8_continuous_m1_results.csv")
  
  specific_oracles_test <- res_oracles_test[, .(
    positivity,
    parameter,
    type,
    psi_specific = psi,
    target = get_target(method)
  )]
  
  
  standard_oracle_test <- specific_oracles_test[target == "standard", .(
    positivity,
    psi_standard = psi_specific
  )]
  
  specific_oracles_test
  standard_oracle_test
```



```{r}
estimator_simulation <- function(
    is_discrete,
    sample_sizes,
    m,
    nuisance,
    oracles_results_filename
) {
  
  # timing this code chunk
  tic()
  
  type_label <- if (is_discrete) "discrete" else "continuous"
  
  # loading precomputed oracles
  res_oracles <- fread(oracles_results_filename)
  
  specific_oracles <- res_oracles[, .(
    positivity,
    parameter,
    type,
    psi_specific = psi,
    target = get_target(method)
  )]
  
  
  standard_oracle <- specific_oracles[target == "standard", .(
    positivity,
    psi_standard = psi_specific
  )]
  
  # iterating over sample sizes
  for (n in sample_sizes) {
    
    n_label <- paste0("n1e", log10(n))
    results <- list()
    
    # iterating over simulation processes
    for (name in names(sim_processes)) {
      cat(sim_titles[name], "\n")
      
      m_results <- vector("list", m)
      
      # iterating over monte carlo draws
      for (i in 1:m) {
        sim <- sim_processes[[name]](n, is_discrete = is_discrete)
        
        # estimator results
        res_estimators <- rbindlist(lapply(estimators, function(estimator) {
          run_estimators(sim, name, estimator, alpha_vals, delta_vals, nuisance)
        }), fill = TRUE)
        
        # store results
        res_estimators[, `:=`(positivity = name, sample_size = n, draw = i)]
        m_results[[i]] <- res_estimators
      }
      
      # combining monte carlo draws
      m_results <- rbindlist(m_results)
      m_results[, target := get_target(method)]
      
      # including oracle results
      m_results <- merge(
        m_results,
        specific_oracles,
        by = c("positivity", "target", "parameter", "type"),
        all.x = TRUE
      )
      
      m_results <- merge(
        m_results,
        standard_oracle,
        by = "positivity",
        all.x = TRUE
      )
      
      
      # aggregate results across monte carlo draws
      aggr_m_results <- m_results[, .(
        mean_psi          = mean(psi), # avg estimated psi
        psi_specific      = mean(psi_specific),
        psi_standard      = mean(psi_standard),
        mean_sd           = mean(se), # mean estimated sd -> make this clear !!!
        sd_psi            = sd(psi), # empirical sd
        sd_ratio          = mean(se) / sd(psi),
        se_psi            = sd(psi)/sqrt(m), # empirical se
        mean_ci95_length  = mean(abs(ci95_upper - ci95_lower)),
        
        specific_bias     = mean(psi - psi_specific),
        specific_coverage = mean(ci95_lower <= psi_specific & psi_specific <= ci95_upper),
        standard_bias     = mean(psi - psi_standard),
        standard_coverage = mean(ci95_lower <= psi_standard & psi_standard <= ci95_upper)
        ),
        by = .(positivity, sample_size, estimator, method, parameter, type)][
          , `:=`(
            specific_coverage_se = sqrt(specific_coverage * (1 - specific_coverage) / m),
            specific_mse         = specific_bias^2 + sd_psi^2,
            standard_coverage_se = sqrt(standard_coverage * (1 - standard_coverage) / m),
            standard_mse         = standard_bias^2 + sd_psi^2
      )]
      results[[name]] <- aggr_m_results
    }
  
    # saving results data
    results <- rbindlist(results, fill = TRUE)
    fwrite(
      results,
      paste0("estimators_", nuisance, "_", n_label, "_", type_label, "_m", m, "_results.csv")
    )
  }
  
  elapsed <- toc(quiet = TRUE)
  cat(
    nuisance, 
    ", sample_sizes =",
    paste(format(sample_sizes, scientific = TRUE), collapse = ", "),
    ", m =", m,
    "~",
    round(elapsed$toc - elapsed$tic, 2),
    "seconds\n"
  )
}
```


## [3] CORRECT

```{r}
estimator_simulation(
  is_discrete = FALSE,
  sample_size = c(1e5),
  m = 500,
  nuisance = "correct",
  oracles_results_filename = "oracles_n1e8_continuous_m1_results.csv"
)
# correct , sample_sizes = 1e+04 , m = 10 ~ 29.27 seconds
# correct , sample_sizes = 1e+05 , m = 500 ~ 11472.15 seconds
```

## [4] MISSPECIFIED g

```{r}
estimator_simulation(
  is_discrete = FALSE,
  sample_size = c(1e5),
  m = 500,
  nuisance = "misspecifiedg",
  oracles_results_filename = "oracles_n1e8_continuous_m1_results.csv"
)
# misspecifiedg , sample_sizes = 1e+05 , m = 500 ~ 11817.23 seconds
# misspecifiedg , sample_sizes = 1e+05 , m = 500 ~ 18670.2 seconds
```


## [5] GAM g

```{r}
estimator_simulation(
  is_discrete = FALSE,
  sample_size = c(1e5),
  m = 500,
  nuisance = "gamg",
  oracles_results_filename = "oracles_n1e8_continuous_m1_results.csv"
)
# gamg , sample_sizes = 1e+05 , m = 500 ~ 20931.3 seconds
```


## [6] MISSPECIFIED Q


```{r}
estimator_simulation(
  is_discrete = FALSE,
  sample_size = c(1e5),
  m = 500,
  nuisance = "misspecifiedQ",
  oracles_results_filename = "oracles_n1e8_continuous_m1_results.csv"
)
# misspecifiedQ , sample_sizes = 1e+05 , m = 500 ~ 12003.95 seconds
```



## [7] MISSPECIFIED

```{r}
estimator_simulation(
  is_discrete = FALSE,
  sample_size = c(1e5),
  m = 500,
  nuisance = "misspecified",
  oracles_results_filename = "oracles_n1e8_continuous_m1_results.csv"
)
# misspecified , sample_sizes = 1e+05 , m = 500 ~ 17472.63 seconds
# misspecified , sample_sizes = 1e+05 , m = 500 ~ 20623.23 seconds
```

## .
## PLOTTING

### PSI



```{r}
plotting_psi_estimates <- function(
    estimators_results_filename,
    n,
    m,
    nuisance_title
) {
  
  tic()
  
  # desired figure width and figure height so that the margin fits
  figw <- 8
  figh <- 5
  
  results_estimators <- fread(estimators_results_filename)
  
  estimator_names <- unique(results_estimators$estimator)
  plots_by_estimator <- list()
  
  
  for (est in estimator_names) {
    
    est_data <- results_estimators[estimator == est]
    plots <- list()
  
    for (name in names(sim_processes)) {
      
      sub_data <- est_data[positivity == name][, psi := mean_psi]
      est_plot_data <- make_plot_data(sub_data)
      
      # match method to color
      methods <- unique(est_plot_data$results_plot$method)
      targets <- get_target(methods)
      cols <- target_colors[targets]
      method_colors <- setNames(cols, methods)
    
      p <- plot_methods(
        est_plot_data,
        paste0(sim_titles[name], " (n = 1e", log10(n), ", m=", m, ")"),
        method_colors,
        y_label = "Target Value",
        bars = TRUE
      )
    
      plots[[name]] <- p
      
      # # saving plot single plot
      # ggsave(
      #   filename = paste0("oracles_", n_label, "_", type_label, "_m", m, "_",  name, ".png"),
      #   plot = p,
      #   width = figw,
      #   height = figh,
      #   dpi = 300
      # )
    }
  
    # combining plots
    p_grid <- plot_grid(
      plots$no,
      plots$prac,
      plots$struc,
      plots$struc_prac,
      nrow = 2
    )
    
    # https://wilkelab.org/cowplot/articles/plot_grid.html
    # adding nuisance title above without changing grid scaling
    title <- ggdraw() +
      draw_label(nuisance_title, fontface = "bold", size = 24, x = 0, hjust = 0) +
      theme(
        plot.margin = ggplot2::margin(0, 0, 0, 0)
      )
    
    # stacking title and grid plot
    p_all <- plot_grid(
      title,
      p_grid,
      ncol = 1,
      rel_heights = c(0.1, 1)
    )
    
    
    results_filename <- sub("^estimators", "", estimators_results_filename)
    results_filename <- sub("_results\\.csv$", "", results_filename)
  
    # saving combined plot
    ggsave(
      filename = paste0(est, results_filename, ".png"),
      plot = p_all,
      width = 2 * figw,
      height = (2 * figh) * 1.1, # adjusting for title height
      dpi = 300
    )
    
    plots_by_estimator[[est]] <- plots
    grid::grid.draw(p_all)
    
  }
  
  toc()
}
```


#### [3]

```{r, fig.width=16, fig.height=11}
plotting_psi_estimates(
  estimators_results_filename = "estimators_correct_n1e5_continuous_m500_results.csv",
  n = 1e5,
  m = 500,
  nuisance_title = "Correct Nuisance Specification"
)
```

#### [4]


```{r, fig.width=16, fig.height=11}
plotting_psi_estimates(
  estimators_results_filename = "estimators_misspecifiedg_n1e5_continuous_m500_results.csv",
  n = 1e5,
  m = 500,
  nuisance_title = "Treatment Mechanism Misspecification"
)
```


#### [5]


```{r, fig.width=16, fig.height=11}
plotting_psi_estimates(
  estimators_results_filename = "estimators_gamg_n1e5_continuous_m500_results.csv",
  n = 1e5,
  m = 500,
  nuisance_title = "Flexible Treatment Estimation"
)
```



#### [6]


```{r, fig.width=16, fig.height=10}
plotting_psi_estimates(
  estimators_results_filename = "estimators_misspecifiedQ_n1e5_continuous_m500_results.csv",
  n = 1e5,
  m = 500,
  nuisance_title = "Outcome Regression Misspecification"
)
```


#### [7]


```{r, fig.width=16, fig.height=10}
plotting_psi_estimates(
  estimators_results_filename = "estimators_misspecified_n1e5_continuous_m500_results.csv",
  n = 1e5,
  m = 500,
  nuisance_title = "Joint Nuisance Misspecification"
)
```



### BIAS, SD, MSE, CP


```{r}
plotting_bias_var_mse <- function(
    estimators_results_filename,
    inference_targ,
    is_discrete,
    n,
    m,
    nuisance_title
  ) {

  tic()
  
  n_label <- paste0("n1e", log10(n))
  type_label <- if (is_discrete) "discrete" else "continuous"
  inference_label <- ifelse(
    inference_targ == "standard",
    "Standard ",
    "Specific "
  )
  
  
  # desired figure width and figure height so that the margin fits
  figw <- 8
  figh <- 5
  
  
  results_filename <- sub("^estimators", "", estimators_results_filename)
  results_filename <- sub("_results\\.csv$", "", results_filename)
  
  results_estimators <- fread(estimators_results_filename)
  
  results_estimators_long <- melt(
    results_estimators,
    id.vars = c("positivity", "sample_size", "estimator", "method", "parameter", "type"),
    measure.vars = c(
      paste0(inference_targ, "_bias"),
      "sd_psi",
      paste0(inference_targ, "_mse"),
      paste0(inference_targ, "_coverage")
    ),
    variable.name = "metric",
    value.name = "value"
  )
  
  # rename metrics
  results_estimators_long[, metric := fcase(
    metric == paste0(inference_targ, "_bias"), "Bias",
    metric == "sd_psi", "SD",
    metric == paste0(inference_targ, "_mse"), "MSE",
    metric == paste0(inference_targ, "_coverage"), "CP"
  )]
  
  estimator_names <- unique(results_estimators$estimator)
  
  for (est in estimator_names) {
    
    metrics <- c("Bias", "SD", "MSE", "CP")
    plots <- list()
    sum_plots <- list()
    
    # match method to color
    methods <- unique(results_estimators_long[estimator == est, method])
    targets <- get_target(methods)
    cols <- target_colors[targets]
    method_colors <- setNames(cols, methods)
    
  
    for (name in names(sim_processes)) {
      
      for (metric_name in metrics) {
        
        sub_data <- results_estimators_long[
          positivity == name &
          estimator == est &
          metric == metric_name
        ][, psi := value]
        
        plot_data <- make_plot_data(sub_data)
        
        p <- plot_methods(
          plot_data,
          paste0(sim_titles[name], " (n = 1e", log10(n), ", m=", m, ")"),
          method_colors,
          y_label = paste0(
            ifelse(metric_name == "SD", "", paste0(" ", inference_label)),
            metric_name
          ),
          bars = FALSE
        )
        
        plots[[paste(metric_name, name, sep = "_")]] <- p
      }
      
      
      sum_plot <- plot_grid(
        plots[[paste0("Bias_", name)]],
        plots[[paste0("SD_", name)]],
        plots[[paste0("MSE_", name)]],
        plots[[paste0("CP_", name)]],
        nrow = 4
      )
      
      sum_plots[[name]] <- sum_plot
    }
    
    # combining plots
    p_grid_1 <- plot_grid(
      sum_plots$no,
      sum_plots$prac,
      ncol = 2
    )
    
    p_grid_2 <- plot_grid(
      sum_plots$struc,
      sum_plots$struc_prac,
      ncol = 2
    )
    
    
    # https://wilkelab.org/cowplot/articles/plot_grid.html
    # adding nuisance title above without changing grid scaling
    title <- ggdraw() +
      draw_label(nuisance_title, fontface = "bold", size = 24, x = 0, hjust = 0) +
      theme(
        plot.margin = ggplot2::margin(0, 0, 0, 0)
      )
    
    # stacking title and grid plot
    p_all_1 <- plot_grid(
      title,
      p_grid_1,
      ncol = 1,
      rel_heights = c(0.1, 1)
    )
    
    p_all_2 <- plot_grid(
      title,
      p_grid_2,
      ncol = 1,
      rel_heights = c(0.1, 1)
    )
  
  
    # saving combined plots
    ggsave(
      filename = paste0(
        "performance_no_prac_",
        inference_targ, "_", est, results_filename, ".png"),
      plot = p_all_1,
      width = 2 * figw,
      height = (4 * figh) * 1.1,
      dpi = 300
    )
    
    ggsave(
      filename = paste0(
        "performance_struc_comb_",
        inference_targ, "_", est, results_filename, ".png"),
      plot = p_all_2,
      width = 2 * figw,
      height = (4 * figh) * 1.1,
      dpi = 300
    )
    
    print(p_all_1)
    print(p_all_2)
  }
  
  elapsed <- toc(quiet = TRUE)
  cat(
    "sample_sizes =",
    paste(format(n, scientific = TRUE), collapse = ", "),
    ", m =", m,
    "~",
    round(elapsed$toc - elapsed$tic, 2),
    "seconds\n"
  )
}
```

#### [3] STANDARD


```{r, fig.width=16, fig.height=20}
plotting_bias_var_mse(
  estimators_results_filename = "estimators_correct_n1e5_continuous_m500_results.csv",
  inference_targ = "standard",
  is_discrete = FALSE,
  n = 1e5,
  m = 500,
  nuisance_title = "Correct Nuisance Specification"
)
# sample_sizes = 1e+04 , m = 10 ~ 23.08 seconds
```


#### [3] SPECIFIC


```{r, fig.width=16, fig.height=20}
plotting_bias_var_mse(
  estimators_results_filename = "estimators_correct_n1e5_continuous_m500_results.csv",
  inference_targ = "specific",
  is_discrete = FALSE,
  n = 1e5,
  m = 500,
  nuisance_title = "Correct Nuisance Specification"
)
```






#### [4] STANDARD

```{r, fig.width=16, fig.height=20}
plotting_bias_var_mse(
  estimators_results_filename = "estimators_misspecifiedg_n1e5_continuous_m500_results.csv",
  inference_targ = "standard",
  is_discrete = FALSE,
  n = 1e5,
  m = 500,
  nuisance_title = "Treatment Mechanism Misspecification"
)
```



#### [4] SPECIFIC

```{r, fig.width=16, fig.height=20}
plotting_bias_var_mse(
  estimators_results_filename = "estimators_misspecifiedg_n1e5_continuous_m500_results.csv",
  inference_targ = "specific",
  is_discrete = FALSE,
  n = 1e5,
  m = 500,
  nuisance_title = "Treatment Mechanism Misspecification"
)
```



#### [5] STANDARD


```{r, fig.width=16, fig.height=20}
plotting_bias_var_mse(
  estimators_results_filename = "estimators_gamg_n1e5_continuous_m500_results.csv",
  inference_targ = "standard",
  is_discrete = FALSE,
  n = 1e5,
  m = 500,
  nuisance_title = "Flexible Treatment Estimation"
)
```



#### [5] SPECIFIC


```{r, fig.width=16, fig.height=20}
plotting_bias_var_mse(
  estimators_results_filename = "estimators_gamg_n1e5_continuous_m500_results.csv",
  inference_targ = "specific",
  is_discrete = FALSE,
  n = 1e5,
  m = 500,
  nuisance_title = "Flexible Treatment Estimation"
)
```


#### [6] STANDARD


```{r, fig.width=16, fig.height=20}
plotting_bias_var_mse(
  estimators_results_filename = "estimators_misspecifiedQ_n1e5_continuous_m500_results.csv",
  inference_targ = "standard",
  is_discrete = FALSE,
  n = 1e5,
  m = 500,
  nuisance_title = "Outcome Regression Misspecification"
)
```


#### [6] SPECIFIC


```{r, fig.width=16, fig.height=20}
plotting_bias_var_mse(
  estimators_results_filename = "estimators_misspecifiedQ_n1e5_continuous_m500_results.csv",
  inference_targ = "specific",
  is_discrete = FALSE,
  n = 1e5,
  m = 500,
  nuisance_title = "Outcome Regression Misspecification"
)
```


#### [7] STANDARD


```{r, fig.width=16, fig.height=20}
plotting_bias_var_mse(
  estimators_results_filename = "estimators_misspecified_n1e5_continuous_m500_results.csv",
  inference_targ = "standard",
  is_discrete = FALSE,
  n = 1e5,
  m = 500,
  nuisance_title = "Joint Nuisance Misspecification"
)
```


#### [7] SPECIFIC


```{r, fig.width=16, fig.height=20}
plotting_bias_var_mse(
  estimators_results_filename = "estimators_misspecified_n1e5_continuous_m500_results.csv",
  inference_targ = "specific",
  is_discrete = FALSE,
  n = 1e5,
  m = 500,
  nuisance_title = "Joint Nuisance Misspecification"
)
```




### .
### CP TABLE


```{r}
results_estimators <- fread(paste0("estimators_", n_label, "_", type_label, "_m", m, "_results.csv"))

tab <- results_estimators[, .(
  positivity,
  estimator,
  method,
  parameter,
  type,

  coverage_ind = individ_coverage,
  coverage_full = full_coverage,
  ci_length = mean_ci95_length,

  sd_emp = sd_psi, # empirical sd
  sd_est = mean_sd, # mean estimated sd
  sd_ratio = sd_ratio # mean(sd) / sd(psi)
)]


setnames(tab, c(
  "positivity", "estimator", "method", "parameter", "type",
  "coverage_ind", "coverage_full", "ci_length",
  "sd_emp", "sd_est", "sd_ratio"
), c(
  "Positivity", "Estimator", "Method", "Param", "Type",
  "CovInd", "CovFull", "CI Width",
  "SD Emp.", "SD Est.", "Ratio"
))


tabs <- split(tab, tab$Estimator)
# tabs <- tabs[, !"estimator", with = FALSE]


 
lapply(names(tabs), function(est) {
  cat("\n\n\\textbf{Estimator:", est, "} \n\n")

  est_dt <- tabs[[est]][, !c("Estimator", "Type"), with = FALSE]
  
  print(nrow(est_dt))
  
  print(
    kable(est_dt, format = "html", booktabs = TRUE, digits = 3) %>% 
    kable_styling(
      bootstrap_options = c("striped", "hover"),
      full_width = FALSE
    ) %>%
      row_spec(0, background = "white") %>%
      row_spec(1:nrow(est_dt), background = "white")
  )
  
  writeLines(
    kable(
      est_dt,
      format = "latex",
      booktabs = TRUE,
      longtable = TRUE,
      digits = 3,
      caption = "Simulation results for ...",
      label = "tab:results"
    ) %>% 
    kable_styling(
      latex_options = c("hold_position")
    ),
  paste0(est, "_results.tex")
  )

})

# tab <- gsub(
#   "\\\\begin\\{longtable\\}\\{",
#   "\\\\begin{ltablex}{\\\\textwidth}{",
#   tab
# )
# 
# tab <- gsub(
#   "\\\\end\\{longtable\\}",
#   "\\\\end{ltablex}",
#   tab
# )


# collapse_rows(columns = 1, latex_hline = "major")

# writeLines(
#   kable(tab, format = "latex", booktabs = TRUE, digits = 3) %>%
#     kable_styling(latex_options = c("striped", "hold_position")),
#   "table_results.tex"
# )
```






# .

# JUNKYARD

## PS ESTIMATION METHODS FOR STRUCTURAL VIOLATIONS

```{r, fig.width=8, fig.height=5}
# # support indicator
# dd[, support := as.integer(any(A == 1)), by = W]

is_discrete = FALSE

dd <- sim_no(1e4, is_discrete = is_discrete)$data


# parametric misspecification
fit_log <- glm(A ~ I(W^2), family = binomial, data = dd)
dd$gg1_hat_mis <- predict(fit_log, type = "response")


fit_gam <- gam(A ~ s(W), family = binomial, data = dd)
dd$gg1_hat_gam <- predict(fit_gam, type = "response")



if (is_discrete) {
  W_out <- (dd$W == 3)
} else {
  W_out <- (2 < dd$W & dd$W < 3)
}


ggplot(dd, aes(x = W, color = factor(A))) +
  
  geom_jitter(
    aes(y = A),
    height = 0.05,
    size = 1,
    alpha = 0.1
  ) +
  
  geom_point(
    aes(
      y = ifelse(W_out, 0, plogis(-2 +  W)),
      color = "True PS"
    ),
    size = 0.5,
    alpha = 0.1) +
  
  geom_point(
    aes(
      y = gg1_hat_mis,
      color = "Misspecified PS"
    ),
    size = 0.5,
    alpha = 0.1
  ) +
  
  geom_point(
    aes(
      y = gg1_hat_gam,
      color = "GAM PS"
    ),
    size = 0.5,
    alpha = 0.1
  ) +
  
  scale_color_manual(
    values = c(
      "0" = "red",
      "1" = "blue",
      "True PS" = "green",
      "Misspecified PS" = "black",
      "GAM PS" = "magenta"
    )
  ) +
  
  labs(
    y = "Received treatment and P(A = 1 | W)",
    color = "A",
    title = "Propensity Score Estimation"
  ) + 
  
  theme_light() +
  theme(
    plot.title = element_text(face = "bold", hjust = 0),
    plot.title.position = "plot",
    panel.border = element_blank(),
    legend.title = element_blank()
  ) +
  
  guides(
  color = guide_legend(
    override.aes = list(size = 4, alpha = 0.5)
  )
)
```




## TESTING TMLE



```{r}
tic()

n <- 1e5
m <- 50
is_discrete = FALSE


alph <- 1e-6
delt <- 10
    

sim_process_results <- list()

for (name in names(sim_processes)) {
  cat(sim_titles[name], "\n")
  
  m_results <- vector("list", m)
  
  for (i in 1:m) {
    # getting simulated data
    sim <- sim_processes[[name]](n, is_discrete = is_discrete)
    
    dd <- sim$data
    orac <- sim$oracle_full
    
    # estimating nuisance parameters
    # treatment mechanism
    
    # fitg <- glm(A ~ W, family = binomial, data = dd)
    # g1_hat <- predict(fitg, type = "response")
    
    # fitg <- glm(A ~ W + I(W^2), family = binomial, data = dd)
    # g1_hat <- predict(fitg, type = "response")
    
    fit_gam <- gam(A ~ s(W), family = binomial, data = dd)
    g1_hat <- predict(fit_gam, type = "response")
    
    # outcome regeression
    fitQ <- lm(Y ~ A + W, data = dd)
    
    dd0 <- copy(dd)[, A := 0]
    dd1 <- copy(dd)[, A := 1]
    
    QA_hat <- predict(fitQ, dd, type = "response")
    Q0_hat <- predict(fitQ, dd0, type = "response")
    Q1_hat <- predict(fitQ, dd1, type = "response")
    
    iptw <- iptw_ips(dd, g1_hat, QA_hat, Q1_hat, Q0_hat, delt)$psi_hat
    hajek <- iptw_hajek_ips(dd, g1_hat, QA_hat, Q1_hat, Q0_hat, delt)$psi_hat
    ose <- onestep_ips(dd, g1_hat, QA_hat, Q1_hat, Q0_hat, delt)$psi_hat
    tmle <- tmle_ips(dd, g1_hat, QA_hat, Q1_hat, Q0_hat, delt)$psi_hat
      
    m_results[[i]] <- data.table(
      positivity = name,
      iptw = iptw,
      hajek = hajek,
      ose = ose,
      tmle = tmle,
      orac = orac
    )
  }
  
  
  sim_process_results[[name]] <- rbindlist(m_results)
  
}

all_results <- rbindlist(sim_process_results, idcol = "positivity")

aggr_all_results <- all_results[, .(
  # mean_psi_iptw = mean(iptw),
  # mean_psi_hajek = mean(hajek),
  # mean_psi_ose = mean(ose),
  # mean_psi_tmle = mean(tmle),
  # orac_psi = mean(orac),
  bias_iptw = mean(iptw - orac),
  bias_hajek = mean(hajek - orac),
  bias_ose = mean(ose - orac),
  bias_tmle = mean(tmle - orac)
  ), by = positivity]

print(format(aggr_all_results, scientific = TRUE))


toc()

# standard target


# correctly specified paramtric treatment glm(A ~ W)
# positivity   bias_iptw       bias_hajek      bias_ose        bias_tmle      
# [1,] "no"         "-2.200897e-04" " 1.612533e-04" " 9.093716e-05" " 9.020880e-05"
# [2,] "prac"       "-2.632797e-04" "-1.376681e-03" "-1.191918e-03" "-1.171793e-03"
# [3,] "struc"      " 3.391491e-02" "-7.829624e-03" "-2.021762e-04" "-1.955658e-04"
# [4,] "struc_prac" " 1.841514e-01" "-2.274085e-02" "-7.913215e-04" "-3.098037e-04"
# 46.589 sec elapsed


# misspecified paramtric treatment glm(A ~ W + I(W^2))
# positivity   bias_iptw       bias_hajek      bias_ose        bias_tmle      
# [1,] "no"         "-8.335492e-05" "-9.440388e-05" "-9.183303e-05" "-9.198529e-05"
# [2,] "prac"       "-1.257038e-03" "-1.469970e-03" "-1.420637e-03" "-1.423707e-03"
# [3,] "struc"      " 4.651730e-02" "-5.478072e-03" "-2.315175e-04" "-2.014539e-04"
# [4,] "struc_prac" " 4.255706e-02" "-3.810418e-03" " 7.612329e-04" " 6.773247e-04"
# 49.369 sec elapsed


# flexible model treatment gam(A ~ s(W))
# positivity   bias_iptw       bias_hajek      bias_ose        bias_tmle      
# [1,] "no"         "-1.896623e-04" "-1.896048e-04" "-1.876008e-04" "-1.879018e-04"
# [2,] "prac"       "-1.344508e-03" "-1.284189e-03" "-1.282467e-03" "-1.282561e-03"
# [3,] "struc"      "-8.994253e-02" "-3.404255e-03" " 5.954887e-04" " 6.639964e-04"
# [4,] "struc_prac" "-7.838256e-02" "-3.417496e-03" " 8.036139e-05" " 8.174534e-05"
# 180.334 sec elapsed



# ips specific target


# correctly specified paramtric treatment glm(A ~ W)
# positivity   bias_iptw       bias_hajek      bias_ose        bias_tmle      
# [1,] "no"         "-1.984425e-05" "-5.590579e-05" "-5.095447e-05" "-4.916473e-05"
# [2,] "prac"       "-1.567359e-03" "-1.461340e-03" "-1.482914e-03" "-1.430938e-03"
# [3,] "struc"      " 3.437619e-02" "-7.318803e-03" " 2.056717e-04" " 2.282693e-04"
# [4,] "struc_prac" " 1.842112e-01" "-2.277509e-02" "-3.308085e-04" "-4.329055e-05"
# 159.583 sec elapsed


# misspecified paramtric treatment glm(A ~ W + I(W^2))
# positivity   bias_iptw       bias_hajek      bias_ose        bias_tmle      
# [1,] "no"         " 4.520703e-04" " 4.605753e-04" " 4.574500e-04" " 4.574378e-04"
# [2,] "prac"       "-1.131845e-03" "-8.489902e-04" "-9.191185e-04" "-9.312353e-04"
# [3,] "struc"      " 4.651241e-02" "-5.550197e-03" "-2.596523e-04" "-2.539687e-04"
# [4,] "struc_prac" " 3.995713e-02" "-5.714597e-03" "-1.266851e-03" "-9.638932e-04"
# 209.719 sec elapsed


# flexible model treatment gam(A ~ s(W))
# positivity   bias_iptw       bias_hajek      bias_ose        bias_tmle      
# [1,] "no"         "-2.324931e-04" "-2.237528e-04" "-2.233670e-04" "-2.234498e-04"
# [2,] "prac"       "-8.112450e-04" "-6.753817e-04" "-6.958747e-04" "-6.969559e-04"
# [3,] "struc"      "-9.100196e-02" "-4.370919e-03" "-3.298970e-04" "-6.947526e-03"
# [4,] "struc_prac" "-7.995843e-02" "-5.249841e-03" "-1.658994e-03" "-1.974849e-03"
# 873.071 sec elapsed



```



```{r}
# DIFFERENT SAMPLING PROBABILITIES

# W = sample(0:4, size=n, replace=TRUE, prob=c(0.5, 0.1, 0.1, 0.1, 0.2))
# W = sample(0:4, size=n, replace=TRUE, prob=c(0.2, 0.1, 0.1, 0.1, 0.5))
```

```{r}
# TREATMENT COVARIATE INTERACTIONS

# dt[, Y := rbinom(.N, 1, 0.4 + 0.2*A*(W >= 2))]
```

```{r}
# # RIT AND TRUNCATED IPTW ORACLE
# 
# # data generation with structural positivity violation
# W = sample(0:4, size=n, replace=TRUE)
# p = plogis(-2 +  W)
# W_out = 3
# p[W == W_out] = 0
# A = rbinom(n, size = 1, prob = p)
# Y = rbinom(n, size = 1, prob = 0.3 + 0.3 * A + 0.05 * W)
# 
# # rit estimand
# d <- ifelse(W %in% W_out, 0, 1)
# mean(0.3 + 0.3 * d + 0.05 * W) - mean(Y)
# 
# 
# n <- length(W)
# n1 <- sum(W == W_out)
# n2 <- sum(W != W_out)
# 
# (n1/n) * mean((0.3 + 0.3 * 0 + 0.05 * W)[W == W_out]) + (n2/n) * mean((0.3 + 0.3 * 1 + 0.05 * W)[W != W_out]) - mean(Y)
# 
# # the first term is the difference between rit and truncated iptw
# (n1/n) * mean((0.3 + 0.3 * 0 + 0.05 * W)[W == W_out])
# 
# 
# # iptw truncated
# alpha_grid <- c(1e-6, 0.01, 0.02, 0.03, 0.04, 0.05)
# 
# psi_vals <- sapply(alpha_grid, function(alpha) {
#   g1_trunc_hat <- pmax(p, alpha)
#   mean(A / g1_trunc_hat * Y) - mean(Y)
# })
# 
# gg1_trunc_hat <- pmax(p, alpha)
# psi_vals
# # truncation does not contribute as A == 0
# 
# n <- length(W)
# 
# n2/n * mean(A[W != W_out] / gg1_trunc_hat[W != W_out] * Y[W != W_out]) - mean(Y)
```



```{r}
# # SINGLE LARGE RUN TARGET PARAMETER SIMULATION

# target_parameter_simulation <- function(is_discrete, n) {
#   # timing this function
#   tic()
#   
#   # desired figure width and figure height so that the margin fits
#   figw <- 8
#   figh <- 5
# 
#   type_label <- if (is_discrete) "discrete" else "continuous"
#   n_label_oracle <- paste0("n1e", log10(n))
#   
#   
#   results <- list()
#   plots <- list()
#   
#   
#   for (name in names(sim_processes)) {
#     # cat(sim_titles[name], "\n")
#     
#     sim <- sim_processes[[name]](n, is_discrete = is_discrete)
#     
#     res <- run_oracles(sim, alpha_vals, delta_vals)[, positivity := name]
#     results[[name]] <- res
#     oracle_plot_data <- make_plot_data(res)
#     
#     # match method to color
#     methods <- unique(oracle_plot_data$results_plot$method)
#     targets <- get_target(methods)
#     cols <- target_colors[targets]
#     method_colors <- setNames(cols, methods)
#     
#     
#     p <- plot_methods(
#       oracle_plot_data,
#       paste0(sim_titles[name], " (n = 1e", log10(n), ")"),
#       method_colors,
#       y_label = "Target Value",
#       bars = FALSE
#     )
#     
#     plots[[name]] <- p
#     
#     # saving plot
#     ggsave(
#       filename = paste0("oracles_", n_label_oracle, "_", type_label, "_", name, ".png"),
#       plot = p,
#       width = figw,
#       height = figh,
#       dpi = 300
#     )
#   }
#   
#   
#   # saving results data
#   results <- rbindlist(results, fill = TRUE)
#   fwrite(results, paste0("oracles_", n_label_oracle, "_", type_label, "_results.csv"))
#   
#   # combining plots
#   p_all <- plot_grid(
#     plots$no,
#     plots$prac,
#     plots$struc,
#     plots$struc_prac,
#     nrow = 2
#   )
#   
#   # saving combined plot
#   ggsave(
#     filename = paste0("oracles_", n_label_oracle, "_", type_label, "_all.png"),
#     plot = p_all,
#     width = 2 * figw,
#     height = 2 * figh,
#     dpi = 300
#   )
#   
#   print(p_all)
#   
#   elapsed <- toc(quiet = TRUE)
#   cat("n =", n, "~", round(elapsed$toc - elapsed$tic, 2), "seconds\n")
# }
# 
# 
# target_parameter_simulation(is_discrete = FALSE, n = 1e7)
# # n = 1e+06 ~ 5.55 seconds
# # n = 1e+07 ~ 26.9 seconds
```


